Quantum Interval-Valued Probability: Measurement and Probability

### 2017-11-07 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

\begin{proof}To prove this theorem, we need to construct a QIVPM
on some Hilbert space, and verify that there are no states that are
consistent with it on all possible events. Assume a Hilbert space
of dimension~$d$ with orthonormal basis $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} $
and $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
For $i=1,\ldots,d-1$, let $\ket{i'}=\left(\ket{0}+\ket{i}\right)/\sqrt{2}$.
The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
Hence,

@@

$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace

@@

$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace

@@

>>>>

\begin{proof}To prove this theorem, we need to construct a QIVPM
on some Hilbert space, and verify that there are no states that are
consistent with it on all possible events. Assume a Hilbert space
of dimension~$d$ with orthonormal basis $\left\{ \ket{0},\ket{1},\ldots,\ket{d-1}\right\} $
and $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $.
For $i=1,\ldots,d-1$, let $\ket{i'}=\left(\ket{0}+\ket{i}\right)/\sqrt{2}$.

@@

$\mathbb{0}$, $\proj{0}$, $\proj{i'}$ & $\imposs$\tabularnewline\addlinespace

@@

$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{i'}$ & $\necess$\tabularnewline\addlinespace

@@

The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
Hence, a set of projections $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{}$.
